\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} 
\moderncvcolor{blue}
\definecolor{mcvblue}{rgb}{0.22,0.45,0.70}
\usepackage[scale=0.75]{geometry}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

% == Personal Data ==
\name{Brandy}{Sandrowicz}
\title{Software Developer}
\phone[mobile]{+1 647 882 2056}
\email{brandy@sandrowicz.org}
\social[github]{bsandrow}

\begin{document}
\makecvtitle

\section{Education}

\cventry{Aug 2005}{Bachelor of Computer Science in Engineering}{University of Michigan}{}{}{}


\section{Experience}

\cventry[1.75em]{2018--2023}{Software Developer}{d1g1t Inc.}{Toronto}{}{%
Financial Software for Money Management Firms\newline{}%
\begin{itemize}%
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built a risk level reporting system for money managers with the support of company's financial engineers.
%\item Built a risk level reporting system for money managers with the support of company's financial engineers.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Worked on both the Python backend and the React front-end systems.
%\item Worked on both the Python backend and the React front-end systems.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built and maintained a system that capable of rebalancing 1000's of financial accounts to match user specified parameters while taking into account various trading restrictions.
%\item Built and maintained a system that capable of rebalancing 1000's of financial accounts to match user specified parameters while taking into account various trading restrictions.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built and maintained a system for managing trades and batches of trades to be sent to trading systems for execution including processing allocation on receipt of trades.
%\item Built and maintained a system for managing trades and batches of trades to be sent to trading systems for execution including processing allocation on receipt of trades.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Maintained a system that managed transactions for all customer accounts and built them into various levels of reporting for both money managers and their clients.
%\item Maintained a system that managed transactions for all customer accounts and built them into various levels of reporting for both money managers and their clients.
\end{itemize}%
\vspace{3mm}%
\textbf{Technologies Used:} Docker, PostgreSQL, MongoDB, ElasticSearch, Python, AWS, Django, Django Rest Framework, Celery, Redis, React.js, JavaScript
}

\cventry[1.75em]{2013--2018}{Lead Software Developer}{Sowingo.com Corp.}{Toronto}{}{%
Dental Supply Management and Marketplace\newline{}%
\begin{itemize}%
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built an eCommerce platform allowing sales from 3rd party vendors from the ground-up.
%\item Built an eCommerce platform allowing sales from 3rd party vendors from the ground-up.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built an inventory management system with specialization in tracking oral surgery supplies from scratch.
%\item Built an inventory management system with specialization in tracking oral surgery supplies from scratch.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built single page app administration system site admins and 3rd party vendors.
%\item Built single page app administration system site admins and 3rd party vendors.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Built a custom PDF generation system for creating shelving labels.
%\item Built a custom PDF generation system for creating shelving labels.
\end{itemize}%
\vspace{3mm}%
\textbf{Technologies Used:} PostgreSQL, MySQL, Amazon Web Services, Flask-RESTful, Python, Flask, Nginx, Ubuntu Linux, ElasticSearch, SQLAlchemy, Stripe, AngularJS 1.x, GulpJS, GruntJS, Angular-Material, HTML, CSS, JavaScript, EmberJS, Bootstrap, LESS, Sass, git, TravisCI, py.test
}

\cventry[1.75em]{2008--2012}{Software Developer}{Rentrak Corp.}{Portland and Toronto}{}{%
Media data analysis and auditing\newline{}%
\begin{itemize}%
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Developed cross-platform application in Groovy to interact with POS systems and transmit transaction information back to central server.
%\item Developed cross-platform application in Groovy to interact with POS systems and transmit transaction information back to central server.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Developed internal CRM to facilitate multiple business units' interactions with customers, including an email gateway, threaded comments, and porting of legacy CRM data.
%\item Developed internal CRM to facilitate multiple business units' interactions with customers, including an email gateway, threaded comments, and porting of legacy CRM data.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Maintained legacy internal applications (including GUIs in Java 1.3, and 'green screens' in C), including adding new features as required.
%\item Maintained legacy internal applications (including GUIs in Java 1.3, and 'green screens' in C), including adding new features as required.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Ported competing system (obtained via acquisition) within existing systems, including data import, reporting system changes and data warehousing.
%\item Ported competing system (obtained via acquisition) within existing systems, including data import, reporting system changes and data warehousing.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Optimized database access as volume passed thresholds that reduced performance to unacceptable levels.
%\item Optimized database access as volume passed thresholds that reduced performance to unacceptable levels.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Implemented marketing materials admin interface in HTML/JS, including drag-and-drop sorting.
%\item Implemented marketing materials admin interface in HTML/JS, including drag-and-drop sorting.
\item[$\textcolor{mcvblue}{\textbf{\guillemetright}}$] Created internal release tool on top of git with Python/Django.
%\item Created internal release tool on top of git with Python/Django.
\end{itemize}%
\vspace{3mm}%
\textbf{Technologies Used:} Linux (CentOS), MS Windows, Unify, Oracle, PostgreSQL, Java, C, Groovy, Perl, Python, Pro*C, Vim, Emacs, Apache, Nginx, Django, SQL*Plus
}


\section{Languages}
\cvskillhead[-0.1em]%
\cvskillentry*{Language:}{4}{Python}{10}{Worked with Python building web APIs for JavaScript front-ends in addition to multiple layers of infrastructure supporting these APIs.}
\cvskillentry*{}{3}{JavaScript}{10}{Worked on front-end apps using both AngularJS 1.x and ReactJS.}
\cvskillentry*{}{3}{Perl}{4}{Worked with Perl 5.8/5.10 backends with some amount of usage of Moose.}
\cvskillentry*{}{2}{C/C++}{4}{Worked on legacy C/C++ applications written in the 90's mostly for maintenance purposes.}
\cvskilllegend*[1em]{}% adjust post spacing

\section{Other}
\cvlistitem{Organizer for Pycon Canada 2013, 2015, and 2016}
\end{document}

% vim:ft=tex